%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
  {Bitkub Online} % Organization
  {Senior Software Engineer (Golang Developer)} % Job title
  {Jan. 2022 - Now} % Date(s)
  {Thailand} % Location
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Made microservice for Bitkub application and www.bitkub.com}
      \item {Design and implement micreservice system e.g. Notification service, User Consent service, User report service, Passkey service, 2FA service, Fee credit service}
      \item {Implement microservice integrate with MySQL, MongoDB, DataDogTracer, OpenTelemetry, RabbitMQ, Vault TOTP}  
      \item {Senior Software Engineer (Jan. 2024 - Now)}
      \item {Software Engineer (Jan. 2022 - Dec. 2023)}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Kasikorn Business-Technology Group (KBTG)} % Organization
    {Software Engineer (Golang/iOS Developer)} % Job title
    {Jun. 2018 - Dec. 2021} % Date(s)
    {Thailand} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Made microservice for K+Shop backend using 'Golang' connecting with MongoDB, Elasticsearch}
        \item {Implement QR Credit Card for K+shop Application}
        \item {Implement SPoC (Software-Based PIN on COTS) for K+shop Application}
        \item {Investigate and Support Incident}
        \item {Scrum Master (Aug. 2020 - Dec. 2021): Facilitate agile ceremony meeting, Resource planning}
        \item {iOS Developer (Jun. 2018 - Dec. 2018): Develop K+SHOP application in a frontend side, UX/UI}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Kasikorn Business-Technology Group (KBTG)} % Organization
  %   {Scrum Master} % Job title
  %   {Aug. 2020 - Dec. 2021} % Date(s)
  %   {Thailand} % Location
  % {
  %   \begin{cvitems} % Description(s) of tasks/responsibilities
  %     \item {Facilitate agile ceremony meeting} %e.g. sprint planning, backlog refinement, daily meeting, sprint review, sprint retrospective
  %     \item {Resource planning}
  %   \end{cvitems}
  % }

%---------------------------------------------------------
  % \cventry
  %   {Kasikorn Business-Technology Group (KBTG)} % Organization
  %   {Software Engineer (iOS Developer)} % Job title
  %   {Jun. 2018 - Dec. 2018} % Date(s)
  %   {Thailand} % Location
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Develop K+SHOP application in a frontend side}
  %       \item {Using VIPER framework}
  %       \item {UX/UI}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  \cventry
    {ExxonMobil} % Organization
    {Cooperative Education program} % Job title
    {Jul. - Dec. 2017} % Date(s)
    {Thailand} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Make chat-bot on SKYPE for Business for Database Administration and Management team call "DBAM Bot" Automatically answer frequently asked questions. Using C\# programming with Visual Studio.}
        \item {Working in global environment with Brazilian co-worker.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {The University of Electro-Communications} % Organization
    {Internship program} % Job title
    {May. - Jun. 2017} % Date(s)
    {Tokyo, Japan} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Cooperative with Japanese students to make gripper robot hand which can catch any object by using SolidWorks to design, 3D printer to printout and control by motors and switches.}
        \item {Exchange knowledge and culture with foreign friends.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
